---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# podcleaner

<!-- badges: start -->
<!-- badges: end -->

The Scottish Post Office directories are annual directories that provide an alphabetical list of a town’s or county’s inhabitants including their forename, surname, occupation and address(es); they provide a solid basis for researching Scotland's family, trade, and town history. A large number of these, covering most of Scotland and dating from 1773 to 1911, can be accessed in digitised form from the [National Library of Scotland](https://digital.nls.uk/directories/). `podcleaner` attempts to clean optical character recognition (OCR) errors in directory records after they've been parsed and saved to "csv" files using a third party tool^[See for example the python [podparser](https://pythonhosted.org/podparser/) library.]. The package further attempts to match records from trades and general directories. See the tests folder for examples running unexported functions. 


## Load
Load general and trades directory samples in memory from "csv" files:

* **Globals**
```{r globals}
library(podcleaner)

directories <- c("1861-1862")

progress <- TRUE; verbose <- FALSE
```

* **General directories**
```{r `load general`}
path_directories <- utils_make_path("data", "general-directories")

general_directory <- utils_load_directories_csv(
  type = "general", directories, path_directories, verbose
)

print.data.frame(general_directory)
```

* **Trades directories**
```{r `load trades`}
path_directories <- utils_make_path("data", "trades-directories")

trades_directory <- utils_load_directories_csv(
  type = "trades", directories, path_directories, verbose
)

print.data.frame(trades_directory)
```


## Clean

Clean records from both datasets:

* **General directories**
```{r `clean general`}
general_directory <-
  general_clean_directory(general_directory, progress, verbose)

print.data.frame(general_directory)
```

* **Trades directories**
```{r `clean trades`}
trades_directory <-
  trades_clean_directory(trades_directory, progress, verbose)

print.data.frame(trades_directory)
```


## Match

Match general to trades directory records:

```{r `match records`}
distance <- TRUE; matches <- TRUE

directory <- combine_match_general_to_trades(
  trades_directory, general_directory, progress, verbose, distance, matches,
  method = "osa", max_dist = 5L
)

print.data.frame(directory)
```

Directory records are compared and eventually matched using a distance metric calculated with the method and corresponding parameters specified in arguments. Under the hood the [fuzzyjoin](https://www.rdocumentation.org/packages/fuzzyjoin/versions/0.1.6) package and the [stringdist_left_join](https://www.rdocumentation.org/packages/fuzzyjoin/versions/0.1.6/topics/stringdist_join) function in particular, help with the matching operations. 


## Save

```{r save, eval = FALSE}
utils_IO_write(directory, "dev", "post-office-directory")

```


